\cvsection{Projects}
\begin{cventries}
%pqdb
%lasermaze
%cdrive
%---------------------------------------------------------
\iffalse
  \cventry
  {\textit{\url{https://github.com/SupaStuff/lasermaze} } }
    {LaserMaze}
    {Feb. 2016}
    {}
    {
      \begin{cvitems}
        \item {Ebook sharing system designed in Software Engineering course}
        \item {Authenticates users and grants them privileges, point system with awards and purchases, enforces cite rules}
        \item {Python was the primary language used with the Django framework}
      \end{cvitems}
    }
\fi
%---------------------------------------------------------

%---------------------------------------------------------
\iftrue
  \cventry
  {\textit{\url{http://ebshare.azurewebsites.net/} } }
    {EBShare}
    {Dec. 2015}
    {}
    {
      \begin{cvitems}
%        \item {Developed this ebook sharing system in Software Engineering course}
        \item {Authenticates users and grants them privileges, point system with awards and purchases, enforces cite rules}
        \item {Uses Python with the Django framework for rapid development}
      \end{cvitems}
    }
\fi
%---------------------------------------------------------

%---------------------------------------------------------
\iffalse
  \cventry
  {\textit{\url{http://www.mariamiamaya.com/} } }
    {Maya's Cooking with Love}
    {July 2015 - Sep. 2015}
    {}
    {
      \begin{cvitems}
        \item {Website for Maria Maya, an Christian author who wishes to share
		  her love for cooking}
        \item {Styled using responsive CSS to accommodate various screen sizes}
        \item {The site features an introduction page, a few sample recipe
		  pages, and a contact page}
      \end{cvitems}
    }
\fi
%---------------------------------------------------------

%---------------------------------------------------------
\iftrue
  \cventry
  {\textit{\url{http://supastuff.github.io/nycHSdir/} } }
    {MyFutureHS}
    {July 2014 - Nov. 2014}
    {}
    {
      \begin{cvitems}
        \item {Searches for High Schools by various criteria such as academics, location, programs, and demographics}
        \item {Visualizes results on the map in the background}
%        \item {Creates a report of selected schools’ statistics}
      \end{cvitems}
    }
\fi
%---------------------------------------------------------

%---------------------------------------------------------
\iffalse
  \cventry
  {\textit{\url{https://github.com/SupaStuff/audioConvert/} } }
    {AudioConvert}
    {Dec. 2013 - Mar. 2014}
    {}
    {
      \begin{cvitems}
        \item {Converts digital audio files between various formats}
        \item {The user can specify what properties to use for naming the output file}
        \item {Submitted for the Honors Enrichment Component project}
      \end{cvitems}
    }
\fi
%---------------------------------------------------------

%---------------------------------------------------------
\iffalse
  \cventry
  {\textit{\url{http://supastuff.github.io/modcodegen/} } }
    {Modcodegen}
    {Nov. 2012}
    {}
    {
      \begin{cvitems}
        \item {Simplifies the use of the weapon modifier codes for Monster Hunter Tri}
        \item {Populates the dropdown boxes with text extracted from a memory dump of the game using JavaScript}
        \item {The YouTube video under “Weapons” demonstrates a roller code used to see all of the sharpness levels}
      \end{cvitems}
    }
\fi
%---------------------------------------------------------

%---------------------------------------------------------
\iftrue
  \cventry
  {\textit{\url{http://dl.dropbox.com/u/24514984/asmPort.exe} } }
    {ASMPort}
    {Aug. 2012}
    {}
    {
      \begin{cvitems}
%        \item {Ports assembly codes from one region to another. Usually from NTSC-U to PAL and vice versa}
        \item {Uses memory dumps from the source and destination region to produce the appropriate codes}
        \item {Wii game modders wrote cheat codes in assembly and ASMPort made them accessible to players in regions other than their own}
      \end{cvitems}
    }
\fi
%---------------------------------------------------------

\end{cventries}
